A Novel Model-Free Learning Approach for Dynamic Target Tracking Problem and its Validation using Virtual Robot Experimentation Platform

### 2020-06-30 paperMIC2020/paperIEEE-MIC2020-V1.tex
Problem setting section has been rewritten

Fig.~\ref{fig:leaderFollowerSetup} shows the setup of the problem that we address in this manuscript. The robot is characterized by its 2D position $(x_k,y_k)$ and orientation $\theta_k\in[-\pi,\pi)$ with respect to global coordinate frame X-Y at discrete time index $k=0,1,\ldots,$ where time $t=kT$ with $T>0$ being the sampling time. The time-varying position of the target is denoted by ${\bf p}_k^{[d]}= [x_k^{[d]},y_k^{[d]}]^T\in\mathbb{R}^2.$  Let the position and orientation (pose) of the robot is denoted by the vector  ${\bf q}_k^T\equiv[x_k,y_k,\theta_k]\in\mathbb{R}^2\times\mathbb{S}^1.$ Without loss of generality, assume that the robot tracks the target's trajectory while maintaining line-of-sight distance (also known as safe distance between the robot and the target) $d>0.$ We emphasize that the mathematical models of both robot and the target are not required in the proposed control technology. For illustration, let us assume that the robot (rear-wheel drive) follows the discrete-time kinematic model described by %
%
\begin{subequations}
  \begin{align}
    \label{eq:robotModelDT}
    x_{k+1} &= x_k +T\nu_k\cos\theta_k\\
    y_{k+1} &= y_k +T\nu_k\sin\theta_k\\
    \theta_{k+1} &= \theta_k + T\frac{\nu_k}{L}\tan\gamma_k
  \end{align}
\end{subequations}
%
where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle of the font castor of the robot (see Fig.~\ref{fig:leaderFollowerSetup}), and $\nu_k\in\mathbb{R}$ is the linear speed. Without loss of generality, this work considers a target modeled by an integrator and its discrete-time kinematic model is described by 
 \begin{align}
   \label{eq:leaderDT}
   \mathbf{p}_{k+1}^{[d]} = \mathbf{p}_k^{[d]} + T_s \, \mathbf{u}_k^{[d]},
 \end{align}  
with $\mathbf{u}_k^{[d]}\in\mathbb{R}^2$ being the control input vector (velocity) that defines the trajectory (considered random in this work) of the target.  In case, the robot modeled by~\eqref{eq:robotModelDT} is described by a differential drive mobile robot, then its left-wheel velocity $\nu_{L,k}$ and right-wheel velocity $(\nu_{R,k})$ are related as 
  \begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/ipe/LFMICSetup.eps}
    }
   \caption{Mobile robot and its dynamic target tracking problem setup.}
   \label{fig:leaderFollowerSetup}
 \end{figure}
 \begin{subequations}
   \begin{align}
     \nu_{k} &= \frac{1}{2}(\nu_{R,k} + \nu_{L,k}),\\
     \omega_{k} &= \frac{1}{\ell}(\nu_{R,k} - \nu_{L,k}) = \frac{\nu_{k}}{L}\tan(\gamma_k) 	
   \end{align}
 \label{eq:robotModel1-DT}
 \end{subequations}
 %
 where $\omega_k = \frac{\nu_k}{L}\tan\gamma_k$ is the angular velocity of the robot's center $(x_k,y_k).$ Let us define the error vector as 
 \begin{multline}
     \label{eq:stateError}
   \mathbf{e}_k = [\rho_k,\tilde\theta_k]^T =
   % [\sqrt{x_e^2+y_e^2},\tilde{\theta_k}]^T = \\
   \begin{bmatrix}
     \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
     (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
     \theta_k^{'} - \theta_k
   \end{bmatrix},
 \end{multline}
% 
 where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right)$ and ${\rho_k}$ the Euclidean distance at time instant $k$ as shown in Fig.~\ref{fig:leaderFollowerSetup}. The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:robotModelDT}~and~\eqref{eq:leaderDT}.

>>>>

Fig.~\ref{fig:leaderFollowerSetup} shows the setup of the problem that we address in this manuscript. The robot is characterized by its 2D position $(x_k,y_k)$ and orientation $\theta_k\in[-\pi,\pi)$ with respect to global coordinate frame X-Y at discrete time index $k=0,1,\ldots,$ where time $t=kT$ with $T>0$ being the sampling time. The time-varying position of the target is denoted by ${\bf p}_k^{[d]}= [x_k^{[d]},y_k^{[d]}]^T\in\mathbb{R}^2.$  Let the position and orientation (pose) of the robot is denoted by the vector  ${\bf q}_k^T\equiv[x_k,y_k,\theta_k]\in\mathbb{R}^2\times\mathbb{S}^1.$ Without loss of generality, assume that the robot tracks the target's trajectory while maintaining line-of-sight distance (also known as safe distance between the robot and the target) $d>0.$ We emphasize that the mathematical models of both robot and the target are not required in the proposed control technology. For illustration, let us assume that the robot (rear-wheel drive) follows the discrete-time kinematic model described by %
%
\begin{subequations}
  \begin{align}
    \label{eq:robotModelDT}
    x_{k+1} &= x_k +T\nu_k\cos\theta_k\\
    y_{k+1} &= y_k +T\nu_k\sin\theta_k\\
    \theta_{k+1} &= \theta_k + T\frac{\nu_k}{L}\tan\gamma_k
  \end{align}
\end{subequations}
%
where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle of the font castor of the robot (see Fig.~\ref{fig:leaderFollowerSetup}), and $\nu_k\in\mathbb{R}$ is the linear speed. Without loss of generality, this work considers a target modeled by an integrator and its discrete-time kinematic model is described by 
 \begin{align}
   \label{eq:leaderDT}
   \mathbf{p}_{k+1}^{[d]} = \mathbf{p}_k^{[d]} + T_s \, \mathbf{u}_k^{[d]},
 \end{align}  
with $\mathbf{u}_k^{[d]}\in\mathbb{R}^2$ being the control input vector (velocity) that defines the trajectory (considered random in this work) of the target.  In case, the robot modeled by~\eqref{eq:robotModelDT} is described by a differential drive mobile robot, then its left-wheel velocity $\nu_{L,k}$ and right-wheel velocity $(\nu_{R,k})$ are related as 
  \begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/ipe/LFMICSetup.eps}
    }
   \caption{Mobile robot and its dynamic target tracking problem setup.}
   \label{fig:leaderFollowerSetup}
 \end{figure}
 \begin{subequations}
   \begin{align}
     \nu_{k} &= \frac{1}{2}(\nu_{R,k} + \nu_{L,k}),\\
     \omega_{k} &= \frac{1}{\ell}(\nu_{R,k} - \nu_{L,k}) = \frac{\nu_{k}}{L}\tan(\gamma_k) 	
   \end{align}
 \label{eq:robotModel1-DT}
 \end{subequations}
 %
 where $\omega_k = \frac{\nu_k}{L}\tan\gamma_k$ is the angular velocity of the robot's center $(x_k,y_k).$ Let us define the error vector as 
 \begin{align}
     \label{eq:stateError}
   \mathbf{e}_k = [\rho_k,\tilde\theta_k]^T=[\sqrt{\tilde{x}_k^2+\tilde{y}_k^2},\tilde{\theta_k}]^T% = \\
   % \begin{bmatrix}
   %   \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
   %   (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
   %   \theta_k^{'} - \theta_k
   % \end{bmatrix},
 \end{align}
% 
 where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right)$
 and ${\rho_k} =\sqrt{\tilde{x}_k^2+\tilde{y}_k^2} $ is the Euclidean distance at time instant $k$ as shown in Fig.~\ref{fig:leaderFollowerSetup} with $\tilde{x}_k = x_k^{[d]} - x_k - d\cos\theta_k^{'},$ $\tilde{y}_k = y_k^{[d]} - y_k - d\sin\theta_k^{'},$ and $\tilde{\theta}_k = \theta_k^{'} - \theta_k.$ The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:robotModelDT}~and~\eqref{eq:leaderDT}.
